%!TEX root = book.tex 
% chktex-file 1
% chktex-file 3
% chktex-file 8
% chktex-file 12
% chktex-file 18
% chktex-file 24
% chktex-file 35 
% chktex-file 42

%-------------------------------------------------------------------%
%-------------------------------------------------------------------%
%-------------------------------------------------------------------%
\chapter{Aspects of set theory}%
\label{cha:aspects_of_set_theory}
%-------------------------------------------------------------------%
%-------------------------------------------------------------------%
%-------------------------------------------------------------------%

Mathematicians' \enquote{stock} set theory, $\zfc$
(Zermelo--Fraenkel set theory $\zf$ plus the Axiom of Choice $\ac$)
doesn't quite have the expressive power one needs for work with categories and higher categories.
The issue ultimately comes down to Cantor's diagonal argument:
there is no surjection of a set onto its powerset.
This is ultimately why no one can contemplate a set of all sets,
and it's also the key to Freyd's observation that
if $C$ is a category and $\kappa$ is the cardinality of its set of arrows,
then $C$ has all $\kappa$-indexed products only if $C$ is a poset.
This, in turn, is what's behind the \enquote{solution set condition}
in representability theorems or the Adjoint Functor Theorem.
Hence one really must distinguish between \enquote{large} and \enquote{small} objects.

One improves matters by passing to von Neumann--Bernays--Gödel set theory ($\nbg$),
which is a conservative extension of $\zfc$.
In $ \nbg $, the formal language consists of the symbols $\in$ and $=$;
a constant $V$; suitable variables;
the usual connectives of first-order logic ($\neg$, $\wedge$, $\vee$, $\implies$, and $\iff$);
and the quantifiers $\forall$ and $\exists$.
The objects of the theory are called \defn{classes}.
A class $ x $ is called a \defn{set} if and only if $x \in V$;
a \defn{proper class} is a class $ X $ such that $ X \notin V $.
We summarize the axioms of $ \nbg $ in informal language:
\begin{description}
	\item[\textbf{Extensionality}] Classes $ X $ and $ Y $ are equal if and only if,
		for any $ z $, one has $ z \in X $ if and only if $ z \in Y $.
	\item[\textbf{Regularity}] For every class $ X $,
		there exists an element $ z \in X $ such that $ z \cap X = \varnothing $.
	\item[\textbf{Infinity}] There is an infinite set.
	\item[\textbf{Union}] If $ x $ is a set, then $ \bigcup x = \bigcup_{z \in x} z $ is a set as well.
	\item[\textbf{Pairing}] If $ x $ and $ y $ are sets, then $ \{x,y\} $ is a set as well.
	\item[\textbf{Powerset}] If $ x $ is a set, then the powerset $ P(x) $ is a set as well.
	\item[\textbf{Limitation of size}] A class $X$ is a proper class if and only if
		there is a bijection between $X$ and $V$.
	\item[\textbf{Class comprehension}] For every first-order formula $ \phi(x) $ with a free variable $ x $ in which the quantifiers are over sets,
		there exists a class $ \{ x \in V : \phi(x) \} $ whose elements are exactly those sets $ x $ such that $ \phi(x) $.
\end{description}

In matters of set theory,
we will generally follow the notations and terminological conventions
of Jech's comprehensive monograph~\citep{Jech2003}.
In particular, $ \Ord $ denotes the proper class of ordinal numbers.
For any ordinal $ \alpha $, the set $ V_{\alpha} $ is defined recursively as follows:
\begin{itemize}
	\item If $ \alpha = 0 $, then $ V_{\alpha} \coloneq \emptyset $;
	\item if $ \alpha = \beta + 1 $ for an ordinal number $ \beta $, then $ V_{\alpha} \coloneq P(V_{\beta}) $;
	\item if $ \alpha $ is a limit ordinal, then $ V_{\alpha} \coloneq \bigcup_{\beta < \alpha} V_{\beta} $.
\end{itemize}
If $ x $ is a set, then the \defn{rank} of $ x $ is the smallest ordinal number $ \alpha $ such that $ x \in V_{\alpha} $.
The proper class $ V $ is then the union $ \bigcup_{\alpha \in \Ord} V_{\alpha} $.

\begin{definition}
	A \defn{large category} $C$ consists of a sequence $(C_n)_{n\in\NN_0}$ of classes,
	along with a family of class maps $ \phi^{\ast} \colon C_m \to C_n $ for each map $ \phi \colon n \to m $,
	subject to the all the formulas that express the statement that $C_n$ is a simplicial class
	that satisfies the inner Kan condition.

	If the large category $C$ contains a full subcategory $ C' \subseteq C $
	such that each $ C'_n $ is a set and such that every object of $ C $ is equivalent to an object of $ C' $,
	then we will call $ C $ a \defn{category}
	or, for emphasis, a \defn{small category}.%
	\footnote{These are sometimes called \defn{essentially small},
	but this distinction is unimportant for us.}
	
	A large category $ C $ is said to be \defn{locally small} if and only if,
	for every subset $ C'_0 \subseteq C_0$,
	the full subcategory $ C' \subseteq C $ spanned by the elements of $ C'_0 $ is small.
	
	Limits and colimits are only considered for functors $ J \to C $ in which
	the $ J $ is a small category.
	Hence when we refer to \defn{all limits} or \defn{all colimits},
	we mean all limits or colimits of diagrams indexed on small categories.
\end{definition}

\begin{eg}
	We shall write $ \Set_V $ for the large category of all sets.
	The objects of $ \Set_V$ are thus precisely the elements of $V$.

	We shall write $ \SS_V $ for the large category of all spaces.
	The objects of $ \SS_V $ are thus precisely the Kan complexes $ \Delta^{\op} \to \Set_V $.

	We shall write $ \Cat_V $ for the large category of all categories.
	The objects of $ \Cat_V $ are thus precisely the weak Kan complexes $ \Delta^{\op} \to \Set_V $.
\end{eg}

The Class Comprehension Axiom Schema implies the \defn{Axiom of Global Choice},
which ensures the existence of a choice function $ \tau \colon V \to V $ such that $ \tau(x) \in x $.
One needs this to make sense of a construction
like \enquote{the} functor $ - \times u \colon C \to C $ for a large category $ C $
with all finite products and a fixed object $ u \in C $.

Here, we will work with $\nbg$ as our base theory,
so that we may speak of proper classes and large categories
whenever the occasion arises.

However, the whole project of category theory and higher category theory turns on the principle that
we want to be able to deal with the collections of all objects of a given kind
as a mathematical object in its own right,
and that the passage up and down these category levels
is a fruitful way to understand even completely \enquote{decategorified} objects.%
\footnote{The \emph{microcosm principle} of Baez--Dolan is a more precise variant of this principle.} 
If we have a large category $C$, we cannot view $C$ itself as an object of a still larger category of all categories,
and that limits the kinds of operations we are permitted to do to $ C $.

To give ourselves the room to pass up and down category levels,
we need to have a hierarchy of \enquote{scales} at which we can work.
These scales will be identified by inaccessible cardinals
or, equivalently, Grothendieck universes (\ref{sec:cardinals}).
The existence of these cardinals is independent of $ \nbg $.

But now a rather different concern arises.
We will also want to have reasonable assurance
that the results we obtain at one scale remain valid at other scales.
We might prefer to prove sentences about
\emph{all} sets, spaces, groups, etc., not just those within a universe.
This sort of \enquote{scale-invariance of truth}
is expressed by a \defn{reflection principle} (\ref{sec:reflection_principles}).
The reflection principle we will use here states roughly that
there is an inaccessible cardinal $ \kappa $ such that
any statement of set theory that holds in the universe $ V_{\kappa} $ holds in $V$ itself.
This is the \defn{Lévy scheme} $ \levy $.
In effect, it permits us to focus our attention on categories (as opposed to large categories).
This axiom schema has a strictly stronger conistency strength than the existence of inaccessible cardinals;
however, its consistency strength is strictly weaker than that of the existence of a single Mahlo cardinal.

%-------------------------------------------------------------------%
%-------------------------------------------------------------------%
\section{Cardinals}%
\label{sec:cardinals}
%-------------------------------------------------------------------%
%-------------------------------------------------------------------%

%-------------------------------------------------------------------%
\subsection{Regularity, smallness, and accessibility}%
\label{sub:regularity_smallness_and_accessibility}
%-------------------------------------------------------------------%

\begin{definition}
	If $ \kappa $ is a cardinal,
	then a set $ S $ is \defn{$ \kappa $-small}
	if and only if $ |S| < \kappa $.
	We shall write $ \Set_{\kappa} \subset \Set_V$
	for the category of $ \kappa $-small sets,
	Thus $ \Set_V $ is the filtered union of the categories $ \Set_{\kappa} $
	over the proper class of regular cardinals.
	
	An infinite cardinal $ \kappa $ is \defn{regular}
	if and only if, for every map $ f \colon S \to T $
	in which $ T $ and every fiber $ f^{-1}\{t\} $ are all $ \kappa $-small,
	the set $ S $ is $ \kappa $-small as well.
	Equivalently, $ \kappa $ is regular if and only if
	$ \Set_{\kappa} \subset \Set_V $ is stable under colimits indexed by $ \kappa $-small posets.
\end{definition}

\begin{eg}
	The $ \aleph $ family of cardinals is defined by
	a function from the class of ordinal numbers
	to the class of cardinal numbers, by transfinite induction:
	\begin{itemize}
		\item The cardinal $ \aleph_0 $ is the ordinal number
			$ \omega $ consisting of all finite ordinals.
		\item For any ordinal $ \alpha $,
			one defines $ \aleph_{\alpha + 1} $ to be
			the smallest cardinal number strictly greater than $ \aleph_{\alpha} $.
		\item For any limit ordinal $ \alpha $,
			one defines $ \aleph_{\alpha} \coloneq \sup \left\{ \aleph_{\beta} : \beta < \alpha \right\} $.
	\end{itemize}

	The countable cardinal $ \aleph_0 $ is regular.
	Every successor cardinal is regular;
	consequently, $ \aleph_n $ for $ n \in \NN $ is regular as well.
	The cardinal $ \aleph_{\omega} $ is the smallest cardinal that is not regular.
\end{eg}

\begin{nul}
	If $ \kappa $ is a regular cardinal,
	then $ \Set_{\kappa} \subset \Set_V $ is the full subcategory
	generated by the singleton $ \{ 0 \}$
	under colimits over $ \kappa $-small posets.
\end{nul}

\begin{definition}
	If $ \kappa $ is a regular cardinal,
	then we shall write $ \SS_{\kappa} \subset \SS_V $
	for the full subcategory generated by $ \{ 0 \} $
	under colimits over $ \kappa $-small posets.

	Similarly, we shall write $ \Cat_{\kappa} \subset \Cat_V $
	for the full subcategory generated 
	by $ \{ 0 \} $ and $ \{ 0 < 1 \} $
	under colimits over $ \kappa $-small posets.
\end{definition}

\begin{eg}
	A set is $ \aleph_0 $-small if and only if it is finite.

	A space is $ \aleph_0 $-small if and only if
	it is weak homotopy equivalent to a simplicial set
	with only finitely many nondegenerate simplices.

	A category $ C $ is $ \aleph_0 $-small if and only if
	it is Joyal equivalent to a simplicial set
	with only finitely many nondegenerate simplices. 
\end{eg}

\begin{definition}
	Let $ \kappa $ be a regular cardinal.
	A category $ \Lambda $ is \defn{$ \kappa $-filtered} if and only if
	it satisfies the following equivalent conditions:
	\begin{enumerate}
		\item For every $ \kappa $-small category $ J $,
			every functor $ f \colon J \to \Lambda $ can be extended
			to a functor $ F \colon J^{\rhd} \to \Lambda $.
		\item For every $ \kappa $-small category $ J $
			and every functer $ H \colon \Lambda \times J \to \SS_V$,
			the natural morphism
			\[
				\colim_{\lambda \in \Lambda} \lim_{j \in J} H(\lambda,j)
				\to
				\lim_{j \in J} \colim_{\lambda \in \Lambda} H(\lambda,j)
			\]
			is an equivalence.
	\end{enumerate}
\end{definition}

\begin{eg}
	For any regular cardinal $ \kappa $,
	the ordinal $ \kappa $, regarded as a category,
	is $ \kappa $-filtered.

	More generally, a poset is $ \kappa $-filtered if and only if
	every $ \kappa $-small subset thereof is dominated by some element.
\end{eg}

\begin{definition}
	A functor $ f \colon C \to D $ between large categories
	will be said to be \defn{$ \kappa $-continuous}
	if and only if it preserves $ \kappa $-filtered colimits.
	
	An object $ X $ of a large locally small category $ C $
	is said to be \defn{$ \kappa $-compact} if and only if
	the functor $ \yo^X \colon C \to \SS_V$ corepresented by $ X $
	(i.e., the functor $ Y \mapsto \Map_C(X,Y) $)
	is $ \kappa $-continuous.
	We write $ C^{\kappa} \subseteq C $
	for the full subcategory of $ \kappa $-compact objects.

	A large category $C$ is \defn{$\kappa$-accessible} if and only if
	$ C $ is locally small, and
	$ C^{\kappa} $ generates $ C $ under $ \kappa $-filtered colimits.
	A $ \kappa $-accessible large category $C$ is \defn{$\kappa$-presentable}%
	\footnote{Some authors use the phrase \defn{$ \kappa $-compactly generated} instead.}
	if and only if $ C^{\kappa} $ has all $ \kappa $-small colimits.
\end{definition}

\begin{eg}
	Let $ \kappa $ be an uncountable regular cardinal.
	Then the following are equivalent for a category $ C $.
	\begin{enumerate}
		\item The category $ C $ is $ \kappa $-small.
		\item The set of equivalence classes of objects of $C$ is $ \kappa $-small,
			and for every morphism $ f \colon X \to Y $ of $ C $ and every $ n \in \NN_0$,
			the set $ \pi_n(\Map_C(X,Y),f) $ is $ \kappa $-small.
		\item The category $ C $ is $ \kappa $-compact as an object of $ \Cat_V $.
	\end{enumerate}
	In particular, a space $ X $ is $ \kappa $-small if and only if
	all its homotopy sets are $ \kappa $-small, if and only if
	it is $ \kappa $-compact as an object of $ \SS_V $.
\end{eg}

\begin{eg}
	The equivalence above is doubly false if $ \kappa = \aleph_0 $.

	First, an $ \aleph_0 $-compact space is a \emph{retract} of
	an $ \aleph_0 $-small space, but 
	it may not be $ \aleph_0 $-small itself.
	If $ X $ is $ \aleph_0 $-compact and \emph{simply connected},
	then $ X $ is $ \aleph_0 $-small.
	The obstruction is the \emph{de Lyra--Wall finiteness obstruction},
	which lies in the reduced $ K_0 $ of the group ring $ \ZZ[\pi_1(X)] $.

	Second, the homotopy sets of an $ \aleph_0 $-small $ X $ space
	are not generally finite.
	By Serre's theorem, if each connected component $ Y \subseteq X $
	has finite fundamental group, then
	its homotopy groups are finitely generated.
	But if $ \pi_1(X) $ isn't finite,
	this too fails;
	for example, $ \pi_3(S^1 \vee S^2) $ is not finitely generated.
\end{eg}

\begin{nul}
	Let $ \kappa \leq \lambda $ be regular cardinals.
	A $ \kappa $-small category is $ \lambda $-small.
	A $ \lambda $-filtered category is $ \kappa $-filtered.
	A $ \kappa $-continuous functor is $ \lambda $-continuous.
	In general, however, there are $ \kappa $-accessible categories
	that are not $ \lambda $-accessible.
\end{nul}

\begin{definition}
	Let $ \kappa $ and $ \lambda $ be regular cardinals.
	We write $ \kappa \ll \lambda $ if and only if,
	for every pair of cardinals $ \kappa_0 < \kappa $ and $ \lambda_0 < \lambda $,
	one has $ \lambda_0^{\kappa_0} < \lambda $.
	Equivalently, $ \kappa \ll \lambda $ if and only if,
	for every $ \kappa $-small set $A$ and every $ \lambda $-small set $ B $,
	the set $ \Map(A, B) $ is $ \lambda $-small.
\end{definition}

\begin{eg}
	For every regular cardinal $ \kappa $, one has $ \aleph_0 \ll \kappa $.
\end{eg}

\begin{nul}
	If $ \kappa \ll \lambda $ are regular cardinals,
	then every $ \kappa $-accessible category is $ \lambda $-accessible.
	Similarly, every $ \kappa $-presentable category is $ \lambda $-presentable.
\end{nul}

\begin{definition}
	A large category $ C $ is \defn{accessible} if and only if
	there exists a regular cardinal $ \kappa $ such that
	$ C $ is $ \kappa $-accessible.
	We shall say that $ C $ is \defn{presentable} if and only if
	there exists a regular cardinal $ \kappa $ such that
	$ C $ is $ \kappa $-presentable.
\end{definition}

\begin{nul}
	A large category is presentable if and only if
	it is accessible and has all colimits.
	A presentable category automatically admits all limits:
\end{nul}

\begin{definition}
	A large category $ C $ is \defn{locally presentable}%
	\footnote{In the $1$-category literature,
		the phrase \emph{locally presentable category} is used for
	what we call \emph{presentable category}.}
	if and only if, every object $ X \in C $
	is contained in a presentable full subcategory $ C' \subseteq C $
	such that the inclusion $ C' \inclusion C $ preserves colimits.
\end{definition}

%-------------------------------------------------------------------%
\subsection{Presheaf categories}%
\label{sub:presheaf_categories}
%-------------------------------------------------------------------%

Let $ C $ be a large category.
Let us imagine what should happen if we seek to make sense in $ \nbg $
of the category $ \PP_0(C) $ of presheaves of sets $ C^{\op} \to \Set_V $.

Right away we encounter a problem:
if the objects of $ C $ form a proper class $ C_ 0 $,
then there is no class of class maps $ \Map(C_0, V) $.
Indeed, on one hand, in $ \nbg $, every element of a class is itself a set,
and on the other hand, a class map $ f \colon C_0 \to V $ cannot be a set.%
\footnote{Worse still, the very large category of classes is not cartesian closed,
so there's no hope of defining $ \Map(C_0, V) $ by means of some other artifice.}

\begin{nul}
	If $ C $ is a small category, then 
	the large category $ \PP_0(C) $ is locally small,
	and it enjoys many of the same good properties enjoyed by $ \Set_V $ itself.
	For every regular cardinal $ \kappa $, it is $ \kappa $-presentable,
	and it is \defn{cartesian closed}:
	for every pair of presheaves $ X, Y \colon C^{\op} \to \Set_V $,
	the morphisms $ X \to Y $ form a presheaf $ \MOR(X, Y) \colon D^{\op} \to \Set_V $.
	The category $ \PP_0(C) $ is a \defn{1-topos}.

	Similarly, the category $ \PP(C) $ of presheaves $ C^{\op} \to \SS_V $
	is a $ \kappa $-presentable topos
	for every regular cardinal $ \kappa $.
\end{nul}

\begin{eg}
	Let $ C $ be a locally small category.
	If $ Y \in C $ is an object,
	then $ \yo_Y \colon C^{\op} \to \Set_V $ is
	the presheaf $ X \mapsto \Map_C(X,Y) $ represented by $ Y $.

	Dually, if $ X \in C $ is an objects,
	then $ \yo^X \colon C \to \Set_V $ is the functor
	$ Y \mapsto \Map_C(X,Y) $ corepresented by $ X $.
\end{eg}

\begin{definition}
	If $ C $ is locally small, then for any small full subcategory $ D \subset C $,
	we may contemplate the category $ \PP_0(D) $ of presheaves $ D^{\op} \to \Set_V $.

	If we have an inclusion of full subcategories $ D' \subseteq D \subset C $, then left Kan extension identifies
	$ \PP_0(D') $ with a full subcategory of $ \PP_0(D) $.
	We can therefore take the (proper-class indexed) filtered union of these categories:
	a \defn{small presheaf} of sets on $ C $ is a functor $ C^{\op} \to \Set_V $
	that is left Kan extended from its restriction to some small full subcategory $ D \subseteq C $.
	
	We write $ \PP^{\sm}_0(C) $ for the large category of small presheaves of sets;
	in other words, $ \PP^{\sm}_0(C) $ is the filtered union $ \bigcup_D \PP_0(D) $
	over the class of small full subcategories of $ C $.
	The category $ \PP^{\sm}_0(C) $ is locally small.

	Similarly, a \defn{small presheaf} (of spaces) is a functor $ C^{\op} \to \SS_V $
	that is left Kan extended from its restriction to some small full subcategory $ D \subseteq C $.
	We write $ \PP^{\sm}(C) $ for the large category of small presheaves.
	Again $ \PP^{\sm}(C) $ is locally small.
\end{definition}

\begin{eg}
	Assume that $ C $ is locally small.
	For any object $ Y \in C $,
	the representable presheaf $ \yo_Y $ is left Kan extended
	from any full subcategory that contains $ Y $.
	In particular, $ \yo_Y $ is small.

	Thus the assignment $ Y \mapsto \yo_Y $ is
	the fully faithful \defn{Yoneda embedding}
	\[
		\yo \colon C \to \PP^{\sm}(C) \period
	\]
\end{eg}

\begin{eg}
	If $ C^{\op} $ is accessible,
	then $ \PP^{\sm}_0(C) $ and $ \PP^{\sm}(C) $
	are the categories of accessible functors
	$ C^{\op} \to \Set_V $ and $ C^{\op} \to \SS_V $, respectively.
\end{eg}

\begin{nul}
	The category $ \PP^{\sm}_0(C) $ does not quite have
	all the same good properties that $ \Set_V $ has, however.
	It has all colimits, but it may not have all limits.
	For example, if $C$ has no nonidentity arrows, then
	$ \PP^{\sm}_0(C) $ has no terminal object.
	
	If $ C^{\op} $ is accessible or small,
	then $ \PP^{\sm}_0(C) $ has all limits.
\end{nul}

\begin{proposition}
	Let $ C $ be a locally small category.
	Then $ \PP^{\sm}(C) $ is the free cocompletion of $ C $.
	That is, for any category $ D $ that has all colimits,
	restriction along the Yoneda embedding $ \yo \colon C \inclusion \PP^{\sm}(C) $
	induces an equivalence of categories
	\[
		\Fun^L(\PP^{\sm}(C), D) \equivalence \Fun(C, D) \period
	\]
\end{proposition}

\begin{definition}
	Let $ \kappa $ be a regular cardinal.
	Let $ C $ be a $ \kappa $-small category.
	A \defn{$ \kappa $-small presheaf} of sets on $ C $ is a functor $ C^{\op} \to \Set_{\kappa} $.
	The category of $ \kappa $-small presheaves of sets will be denoted $ \PP^{\kappa}_0(C) $.

	Similarly, the category of $ \kappa $-small presheaves $ C^{\op} \to \SS_{\kappa} $
	will be denoted $ \PP^{\kappa}(C) $.
\end{definition}

\begin{nul}
	The category $ \PP^{\kappa}_0(C) $ has all $ \kappa $-small colimits, but
	in general, it does not have $ \kappa $-small limits, and
	it is not cartesian closed.
\end{nul}

%-------------------------------------------------------------------%
\subsection{Strong limit and inaccessible cardinals}%
\label{sub:strong_limit_and_inaccessible_cardinals}
%-------------------------------------------------------------------%

\begin{definition}
	One says that $ \kappa $ is a \defn{weak limit cardinal} if and only if,
	for every cardinal $ \xi $,
	if $ \xi < \kappa $, then $ \xi^+ < \kappa $.

	A cardinal $\kappa$ is said to be a \defn{strong limit cardinal} if and only if,
	for every cardinal $ \xi $,
	if $ \xi < \kappa $, then $ 2^{\xi} < \kappa $ as well.
	Equivalently, $ \kappa $ is a strong limit cardinal if and only if,
	for every pair of $ \kappa $-small sets $ X $ and $ Y $,
	the set $ \Map(X, Y) $ of maps $ X \to Y $ is $ \kappa $-small as well. 

	One says that $\kappa$ is \defn{weakly inaccessible} if and only if
	it is a regular, uncountable, weak limit cardinal.

	One says that $\kappa$ is \defn{inaccessible}%
	\footnote{Some authors say \defn{strongly inaccessible} instead of \defn{inaccessible}.}
	if and only if it is a regular, uncountable, strong limit cardinal.
	Equivalently, an uncountable cardinal $ \kappa $ is inaccessible if and only if
	$ \Set_{\kappa} $ has all $ \kappa $-small colimits and is cartesian closed.
	Equivalently again, an uncountable cardinal $ \kappa $ is inaccessible if and only if 
	$ \Set_{\kappa} $ has all $ \kappa $-small colimits and all $ \kappa $-small colimits.
\end{definition}

The Generalized Continuum Hypothesis ($ \gch $) is equivalent to the statement that
the classes of strong and weak limit cardinals coincide,
and similarly the classes of inaccessible and weakly inaccessible cardinal coincide.

\begin{eg}
	A cardinal $ \kappa $ is a weak limit cardinal if and only if,
	for some limit ordinal $ \alpha $, one has $ \kappa = \aleph_{\alpha} $.
\end{eg}

\begin{eg}
	The $\beth$ family of cardinals is defined by a function from the class of ordinal numbers to the class of cardinal numbers.
	It's defined by transfinite induction:
	\begin{itemize}
		\item By definition, $ \beth_0 = \aleph_0 $.
		\item For any ordinal $ \alpha $, one defines $ \beth_{\alpha+1} \coloneq 2^{\beth_{\alpha}} $.
		\item For any limit ordinal $ \alpha $,
			one defines $ \beth_{\alpha} \coloneq \sup \left\{ \beth_{\beta} : \beta < \alpha \right\} $.
	\end{itemize}
	The cardinal $ \beth_{\alpha} $ is the cardinality of $ V_{\omega+\alpha} $.

	The Generalized Continuum Hypothesis ($ \gch $) is equivalent to the statement that
	$ \aleph_{\alpha} = \beth_{\alpha} $ for each ordinal $ \alpha $,	
	
	A cardinal $ \kappa $ is a strong limit cardinal if and only if,
	for some limit ordinal $ \alpha $, one has $ \kappa = \beth_{\alpha} $.

	The cardinal $ \beth_{\omega} $ is thus the smallest uncountable strong limit cardinal.
	It is not an inaccessible cardinal, however, because it is not regular.

	It turns out that an inaccessible cardinal $ \kappa $ is a \defn{$\beth$-fixed point}:
	that is, $ \beth_{\kappa} = \kappa $.
\end{eg}

\begin{definition}
	A regular uncountable cardinal $ \kappa $ is inaccessible if and only if
	one has $ \kappa \ll \kappa $.
\end{definition}

\begin{definition}[\protect{\citep[Exposé I, \S 0 and Appendix]{SGA41}}]%
\label{dfn:uni}
	An uncountable set $\VV$ is a \defn{Grothendieck universe} if it satisfies the following conditions.
	\begin{enumerate}
		\item The set $\VV$ is \defn{transitive}: $X\in Y\in\VV$, then $X\in\VV$ as well.
		\item If $X,Y\in\VV$, then $\{X,Y\}\in\VV$ as well.
		\item If $X\in\VV$, then the powerset $P(X)\in\VV$ as well.
		\item If $A\in\VV$ and $X \colon A \to \VV$ is a map, then
		\[
			\bigcup_{\alpha\in A}X(\alpha) \in \VV
		\]
		as well.
	\end{enumerate}
\end{definition}

Grothendieck universes are essentially the same thing as inaccessible cardinals.
This was effectively proved by Tarski in 1938.
One may also cite Bourbaki.\citep[Exposé I, Appendix]{SGA41}
\begin{proposition}
	If $\kappa$ is an inaccessible cardinal, then
	the set $V_{\kappa}$ of all sets of rank less than $\kappa$ is
	a Grothendieck universe of rank and cardinality $\kappa$.

	If $ V $ is a Grothendieck universe, then
	there exists an inaccessible cardinal $ \kappa $ such that $ V=V_{\kappa} $.
\end{proposition}

\begin{theorem}
	If $ \kappa $ is an inaccessible cardinal,
	then $V_{\kappa} $ models $ \zfc $, and
	$ V_{\kappa+1} $ models $ \nbg $.
	
	Assuming that $ \zfc $ (respectively, $ \nbg $) is consistent, then
	the existence of inaccessible cardinals is not provable
	by methods formalizable in $ \zfc $ (resp., $ \nbg $).
\end{theorem}

\begin{axiom}%
\label{axm:AU}
	The \defn{Axiom of Universes} ($ \au $) is the assertion that
	every cardinal is dominated by an inaccessible cardinal,
	or, equivalently, every set is an element of some Grothendieck universe.
	\defn{Tarski--Grothendieck set theory} is the schema $\tg = \nbg+\au$.
\end{axiom}

%-------------------------------------------------------------------%
\subsection{Higher inaccessibility}%
\label{sub:higher_inaccessibility}
%-------------------------------------------------------------------%

\begin{nul}
	We shall endow an ordinal with its order topology.
	This may be described recursively as follows:
	\begin{itemize}
		\item The ordinal $ 0 $ is the empty topological space.
		\item For any ordinal $ \alpha $ with its order topology,
			the order topology on the ordinal $ \alpha + 1 $
			is the one-point compactification of $ \alpha $.
		\item For any limit ordinal $ \alpha $,
			the order topology is the colimit topology
			$ \colim_{\beta < \alpha} \beta $.
	\end{itemize}
\end{nul}

We will use terminology 
that treats $ \Ord $ itself as a topological space,
even though it is not small.

\begin{definition}
	If $ W \subseteq \Ord $ is a subclass,
	then a \defn{limit point} of $ A $ is
	an ordinal $ \alpha $ such that $ \alpha = \sup (W \cap \alpha) $.
	The class $ W $ will be said to be \defn{closed} if and only if
	it contains all its limit points.

	An \defn{ordinal function} is a class map $ f \colon \Ord \to \Ord $.
	We say that $ f $ is \defn{continuous} if and only if
	its restriction to any subset is continuous.
	Equivalently, $ f $ is continuous if and only if,
	for every subclass $ W \subseteq \Ord $
	and every limit point $ \alpha $ of $ W $,
	the ordinal $ f(\alpha) $ is a limit point of $ f(W) $.

	We say that $ f $ is \defn{normal} if and only if
	it is continuous and strictly increasing.
\end{definition}

\begin{nul}
	If $ f $ is a normal ordinal function,
	then its image is a closed and unbounded class%
	\footnote{This is often abbreviated \defn{club class} in
	set theory literature.}
	of ordinals.
	Conversely, if $ W \subseteq \Ord $ is a closed and unbounded class,
	then we can define a normal ordinal function $ f $ by
	\[
		f(\alpha) = \min \left\{ \gamma \in W : (\forall \beta < \alpha)(f(\beta) < \gamma) \right\} \period
	\]
\end{nul}

\begin{definition}
	Let $ f $ be an ordinal function.
	A regular cardinal $ \kappa $ is said to be
	\defn{$ f $-inaccessible} if and only if,
	for every ordinal $ \alpha$, if $ \alpha < \kappa $,
	then $ f(\alpha) < \kappa $ as well.
\end{definition}

\begin{eg}
	If $ f $ is the ordinal function that carries
	an ordinal $ \alpha $ to the cardinal $ 2^{|\alpha|} $,
	then an $ f $-inaccessible cardinal is precisely
	an inaccessible cardinal.
\end{eg}

\begin{nul}
	Let $ f $ be an increasing ordinal function
	such that for every ordinal $ \beta $, one has $ \beta < f(\beta) $.
	For every ordinal $ \xi $,
	the normal ordinal function $ \alpha \mapsto f^{\alpha}(\xi) $
	in uniquely specified by the requirements that
	$ f^0(\xi) = \xi $ and $ f^{\alpha + 1}(\xi) =f(f^{\alpha}(\xi)) $.

	Jorgenson proves that an $ f $-inaccessible cardinal
	greater than an ordinal $ \xi $
	is precisely a regular cardinal that is a \emph{fixed point}
	for the ordinal function $ \alpha \mapsto f^{\alpha}(\xi) $.
\end{nul}

\begin{eg}
	If $ f $ is the ordinal function $ \beta \mapsto 2^{|\beta|} $,
	then $ f^{\alpha}(\omega) = \beth_{\alpha} $.
	An inaccessible cardinal is thus precisely a regular $ \beth $-fixed point.
	
	If $ f $ is the ordinal function $ \beta \mapsto |\beta|^+ $,
	then $ f^{\alpha}(\omega) = \aleph_{\alpha} $. 
	A weakly inaccessible cardinal is precisely a regular $ \aleph $-fixed  point.
\end{eg}

\begin{axiom}
	The \defn{Lévy scheme} ($ \levy $) is the assertion that
	for every ordinal function $ f $ and every ordinal $ \xi $,
	there exists an $ f $-inaccessible cardinal $ \kappa $ such that $ \xi < \kappa $.
\end{axiom}

\begin{theorem}[\citep{Levy1960, Montague1962, Jorgensen1970}]
	The following are equivalent.
	\begin{enumerate}
		\item The Lévy scheme.
		\item Every normal ordinal function
			has a regular cardinal in its image.
		\item Every closed unbounded subclass $ W \subseteq \Ord $
			contains a regular cardinal.
		\item Every normal ordinal function
			has an inaccessible cardinal in its image.
		\item Every closed unbounded subclass $ W \subseteq \Ord $
			contains an inaccessible cardinal.
	\end{enumerate}
\end{theorem}

\begin{definition}
	Let $ \kappa $ be a regular cardinal.

\end{definition}

\begin{nul}
	The Lévy scheme and its equivalents have gone under various names:
	\enquote{$ \Ord $ is Mahlo}, \enquote{Axiom F}, \enquote{
\end{nul}

%-------------------------------------------------------------------%
\section{Refection principles}%
\label{sec:reflection_principles}
%-------------------------------------------------------------------%

The \defn{Lévy scheme}, $\levy$ was originally proposed by Lévy,\citep{Levy1960}.
Since then essentially the same set theory arrived under different names:

Its suitability for the tasks of category theory was recently emphasized by Mike Shulman \citep{Shulman:2008th}.
It addresses the following informal points.
\begin{enumerate}
	\item We must avoid any of the usual known paradoxes of set theory,
		particularly, the Russell paradox, the Cantor paradox, and the Burali–Forti paradox.
		This is the point that \emph{large objects are genuinely different from small objects}.
		This can be formalised by means of a (relatively modest) large cardinal axiom.
		This is precisely the motivation for the Axiom of the Universe
		as formulated by Grothendieck et al.\citep[Exposé I, \S 0 and Appendix]{SGA41}
	\item At the same time, constructions of objects that involve representability theorems --- for example --- may not be stable under passage to higher universes.%
		\footnote{There are examples of this.
			Waterhouse constructs a presheaf whose fpqc sheafification actually depends upon the universe one is in.
			One may take this as a sign that fpqc sheafification is to be avoided.}
		The axioms of our set theory should formalise the idea that \emph{large objects are different from small objects, but they still behave in the same manner}.
		This is the core of the \defn{Reflection Principle}, which is also the primary insight in Feferman's construction of $\zfc/\SS$.
	\item Though there are genuine (and genuinely relevant) mathematical ideas at work in the Reflection Principle,
		those mathematicians who do not wish to contemplate large cardinal axioms should be able to make use of the assertions made here naively without consequential errors.
		This is achieved by working with an extension of the more familiar \zfc combined with a few rules as to what sort of manoeuvres are permitted with large objects.
\end{enumerate}

We now set about describing the axioms beyond the usual axioms of \zfc we shall employ.
For more details, we refer the reader to Jech's comprehensive text.\citep{Jech2003}

\begin{notation}%
\label{ntn:ZFC}
	We denote by $\mathscr{L}$ the language formal set theory,
	which consists of the symbols $\in$ and $=$; suitable variables; connectives $\neg$, $\wedge$, $\vee$, $\implies$, and $\iff$; and quantifiers $\forall$ and $\exists$.

	We denote by \zfc the theory given by the following axioms and axiom schemata in the language $\mathscr{L}$.
	\begin{enumerate}
		\item Axiom of Extensionality.\citep[p. 4]{Jech2003}
		\item Axiom of Pairing.\citep[p. 6]{Jech2003}
		\item Axiom Schema of Separation.\citep[p. 7]{Jech2003}
		\item Axiom of Union.\citep[p. 9]{Jech2003}
		\item Axiom of Powerset.\citep[p. 9]{Jech2003}
		\item Axiom of Infinity.\citep[p. 12]{Jech2003}
		\item Axiom Schema of Replacement.\citep[p. 13]{Jech2003}
		\item Axiom of Regularity.\citep[p. 63]{Jech2003}
		\item Axiom of Choice.\citep[p. 47]{Jech2003}
	\end{enumerate}
\end{notation}


\begin{axiom}%
\label{axm:Levy}
	We add to the language $\mathscr{L}$ an additional constant $\kappa$,
	and we add the following axioms to $\zfc$ to form \defn{the Lévy scheme} $\levy$.
	\begin{enumerate}
		\item $\kappa$ is an inaccessible cardinal.
		\item \defn{Axiom of Reflection.} For any formula $\phi$, and for any element $x\in V_{\kappa}$, one has
		\[
			\phi(x)\iff \VV_{\kappa}\models\phi[x].
		\]
	\end{enumerate}
\end{axiom}

The Lévy scheme implies $\zfc+\textsc{om}$, where $\textsc{om}$ is the scheme%
\footnote{The notation $\textsc{om}$ is meant to stand for \enquote{\textsc{ord} is Mahlo.}}
asserting that any closed unbounded subclass of $\textsc{ord}$ that is definable from parameters contains an inaccessible cardinal.
On the other hand, if $\zfc+\textsc{om}$ is consistent, then so is $\textsc{Lévy}$.

The Lévy scheme is stronger than the Axiom of Universes ($\textsc{au}$), which asserts that every cadinal is dominated by an inaccessible cardinal;
on the other hand, if $\delta$ is a \emph{Mahlo} cardinal, then $\VV_{\delta}\models\textsc{Lévy}$, so the Lévy scheme is of strictly lower conistency strength than the existence of a single Mahlo cardinal. Among large cardinal axioms, therefore, it appears that $\textsc{Lévy}$ is quite weak.

Finally, it turns out that by adding the axioms for the Lévy scheme, we may do so at the same time we \emph{remove} the Axiom Schema of Replacement and Axiom of Infinity and get an equivalent theory.

%-------------------------------------------------------------------%
\section{Limits, colimits, and cardinals}%
\label{sec:limits_colimits_and_cardinals}
%-------------------------------------------------------------------%

%-------------------------------------------------------------------%
\section{Ultrafilters}%
\label{sec:ultrafilters}
%-------------------------------------------------------------------%

\begin{notation}
	Write $ \Set $ for the category of finite sets.
	Write $ \Fin \subset \Set $ for the full subcategory of finite sets,
	and write $ i $ for the inclusion $ \Fin \inclusion \Set $.
\end{notation}

\begin{definition}
	For any tiny set $ S $, write $ h^S $ for the functor $ \Fin \to \Set $ given by $ I  \mapsto \Map(S, I) $.
	An \defn{ultrafilter} $ \mu $ on $ S $ is a natural transformation
	\[
		\int_S (\cdot) \ d\mu \colon h^S \to i \comma
	\]
	which for any finite set $I$ gives a map
	\[
		\begin{tikzcd}[column sep={1ex}, row sep={0ex}]
			\Map(S, I) \ar[r] & I \\
			f \ar[r, mapsto] & \int_S f \ d \mu
		\end{tikzcd}
	\]

	Write $ \beta (S) $ for the set of ultrafilters on $ S $.
	For any set $ S $, the set $ \beta(S) $ is the set
	\[
		\beta(S) = \lim_{I \in \Fin_{S/}} I \period
	\]
	The functor
	\[
		\beta \colon \Set \to \Set
	\]
	is thus the right Kan extension of the inclusion $ \Fin \inclusion \Set $ along itself.
\end{definition}

\begin{eg}
	Let $ S $ be a set, and let $ s \in S $ be an element.
	The \defn{principal ultrafilter} $ \delta_s $ is then defined so that
	\[
		\int_S f \ d \delta_s = f(s) \period
	\]
\end{eg}

Every ultrafilter on a finite set is principal,
but infinite sets have ultrafilters that are not principal.
To prove the existence of these, let us look at a more traditional way of defining an ultrafilter on a set.

\begin{definition}
	Let $ S $ be a set, $ T \subseteq S$, and $ \mu $ an ultrafilter on $ S $.
	There is a unique \defn{characteristic map} $ \chi_T \colon S \to \{ 0,1 \}$ such that $ \chi_T(s) = 1 $ if and only if $ s \in T $.
	Let us write
	\[
		\mu(T) \coloneq \int_S \chi_T \ d \mu \period
	\]
	
	We say that \defn{$ T $ is $ \mu $-thick} if and only if $\mu(T) = 1$.
	Otherwise (that is, if $ \mu(T) = 0 $), then we say that $ T $ is \defn{$ \mu $-thin}.

	For any $ s \in S$, the principal ultrafilter $ \delta_s $ is the unique ultrafilter relative to which $ \{ s \} $ is thick.
\end{definition}

\begin{scholium}
	If $ S $ is a set and $ \mu $ is an ultrafilter on $ S $, then we can observe the following facts about the collection of thick and thin subsets (relative to $ \mu $):
	\begin{enumerate}
		\item The empty set is thin.
		\item Complements of thick sets are thin.
		\item Every subset is either thick or thin.
		\item Subsets of thin sets are thin.
		\item The intersection of two thick sets is thick.
	\end{enumerate}
	In other words, if $ S $ is a set, then an ultrafilter on $ S $ is tantamount to a Boolean algebra homomorphism $ \PP(S) \to \{0,1\} $.

	It is possible to define ultrafilters on more general posets, and if $ P $ is a Boolean algebra, then an ultrafilter is precisely a Boolean algebra homomorphism $ P \to \{0, 1\} $.
\end{scholium}

\begin{scholium}
	Ultrafilters are functorial in maps of sets.
	Let $ \phi \colon S \to T $ be a map, and let $ \mu $ be an ultrafilter on $ S $.
	The ultrafilter $ \phi_{\ast}\mu $ on $ T $ given by
	\[
		\int_T f \ d (\phi_{\ast}\mu) = \int_S (f \circ \phi) \ d \mu \period
	\]
	For any $ U \subseteq T$, one has in particular
	\[
		(\phi_{\ast} \mu)(U) = \mu (\phi^{-1}(U)) \period
	\]
	Thus $ U $ is $ \phi_{\ast} \mu $-thick if and only if $ \phi^{-1} U $ is $ \mu $-thick.
\end{scholium}

\begin{definition}
	A \defn{system of thick subsets} of $ S $ is a collection $ F \subseteq \PP(S) $ such that for any finite set $ I $ and any partition
	\[
		S = \coprod_{ i \in I } S_i \comma
	\]
	there is a unique $ i \in I $ such that $ S_i \in F $.
\end{definition}

\begin{construction}
	We have seen that an ultrafilter $ \mu $ specifies the system $ F_{\mu} $ of $ \mu $-thick subsets.
	In the other direction, attached to any system $F$ of thick subsets is an ultrafilter $\mu_F$: for any finite set $ I $ and any map $ f \colon S \to I $, the element $ i = \int_S f \ d \mu \in I $ is the unique one such that $ S_i \in F$.

	The assignments $ \mu \mapsto F_{\mu} $ and $ F \mapsto \mu_F $ together define a bijection between ultrafilters on $S$ and systems of thick subsets.
\end{construction}

\begin{definition}
	If $ S $ is a set, and if $ G \subseteq \PP(S) $, then an ultrafilter $ \mu $ is said to be \defn{supported on $ G $} if and only if every element of $G$ is $ \mu $-thick, that is, $ G \subseteq F_{\mu} $.
\end{definition}

\begin{lemma} \label{generateultrafilters}
	Let $ S $ be a set, and let $ G \subseteq \PP(S) $.
	Assume that no finite intersection of elements of $ G $ is empty.
	Then there exists an ultrafilter $ \mu $ on $ S $ supported on $ G $.
\end{lemma}

\begin{proof}
	Consider all the families $ A \subseteq \PP(S) $ with the following properties:
	\begin{enumerate}
		\item $ A $ contains $ G $;
		\item \label{FIP} no finite intersection of elements of $ A $ is empty.
	\end{enumerate}
	By Zorn's lemma there is a maximal such family, $ F $.

	We claim that $ F $ is a system of thick subsets.
	For this, let $ S = \coprod_{i \in I} S_i $ be a finite partition of $ S $.
	Condition \ref{FIP} ensures that at most one of the summands $ S_i $ can lie in $ F $.
	Now suppose that none of the summands $ S_i $ lies in $ F $.
	Consider, for each $ i \in I $, the family $ F \cup \{ S_i \} \subseteq \PP(S) $;
	the maximality of $ F $ implies that none of these families can satisfy Condition \ref{FIP}.
	Thus for each $ i \in I $, there is an empty finite intersection
	$S_i \cap \bigcap_{j = 1}^{n_i} T_{ij} = \varnothing $.
	But this implies that the intersection $ \bigcap_{i \in I}\bigcap_{j = 1}^{n_i} T_{ij} $ is empty, contradicting Condition \ref{FIP} for $ F $ itself.
	Hence at least one -- and thus exactly one -- of the summands $ S_i $ lies in $ F $.
	Thus $ F $ is a system of thick subsets of $ S $.
\end{proof}

\begin{nul}
	It is not quite accurate to say that the Axiom of Choice is \emph{necessary} to produce nonprincipal ultrafilters, but it is true that their existence is independent of Zermelo--Fraenkel set theory.
\end{nul}

\begin{nul}
	If $ \phi $ is a functor $ \Set \to \Set $, then a natural transformation $ \phi \to \beta $ is the same thing as a natural transformation $ \phi \circ i \to i $.
	Please observe that we have a canonical identification $ \beta \circ i = i $.

	It follows readily that the functor $ \beta $ is a monad: the unit $ \delta \colon \id \to \beta $ corresponds to the identification $ {\id} \circ i = i $, and the multiplication $ \mu \colon \beta^2 \to \beta $ corresponds to the identification $ \beta^2 \circ i = i $.

	The unit for the monad $\beta$ structure is the assignment $ s \mapsto \delta_s $ that picks out the principal ultrafilter at a point.

	To describe the multiplication $ \tau \mapsto \mu_{\tau} $, let us write $ T^{\dag} $ for the set of ultrafilters supported on $\{T\}$.
	Now if $ \tau $ is an ultrafilter on $ \beta(S) $, then $ \mu_{\tau} $ is the ultrafilter on $S$ such that
	\[
		\mu_{\tau} ( T ) = \tau ( T^{\dag} ) \period
	\]
\end{nul}

\begin{construction}
	Let $ \categ{Top} $ denote the category of tiny topological spaces.
	If $ S $ is a set, we can introduce a topology on $ \beta(S) $ simply by forming the inverse limit $ \lim_{I \in \Fin_{S/}} I $ in $ \categ{Top} $.
	That is, we endow $ \beta(S) $ with the coarsest topology such that all the projections $ \beta(S) \to I $ are continuous.
	We call this the \defn{Stone topology} on $\beta(S)$.
	By Tychonoff, this limit is a compact Hausdorff topological space.
	This lifts $ \beta $ to a functor $ \Set \to \Top $.
\end{construction}

\begin{nul}
	Let's be more explicit about the topology on $ \beta(S) $.
	The topology on $ \beta(S) $ is generated by the sets $ T^{\dag} $ (for $ T \subseteq S $).
	In fact, since the sets $ T^{\dag} $ are stable under finite intersections, they form a base for the Stone topology on $ \beta(S) $.
	Additionally, since the sets $ T^{\dag} $ are stable under the formation of complements, they even form a base of clopens of $ \beta(S) $.
\end{nul}

\begin{definition} \label{compactaasbetaalgebras}
	A \defn{compactum} is an algebra for the monad $ \beta $.
	Hence a compactum consists of a set $ K $ and a map $ \lambda_K \colon \beta(K) \to K $, which is required to satisfy the usual identities:
	\[
		\lambda_K(\lambda_{K,\ast}\tau) = \lambda_K(\mu_{\tau}) \andeq{} \lambda_K(\delta_s) = s \comma
	\]
	for any ultrafilter $ \tau $ on $ \beta(S) $ and any point $ s \in S $.
	The image $ \lambda_K(\mu) $ will be called the \defn{limit} of the ultrafilter $\mu$.
	We write $ \Comp $ for the category of compacta, and write $\Compfree \subset \Comp $ for the full subcategory spanned by the \defn{free compacta} -- \emph{i.e.}, free algebras for $ \beta $.
\end{definition}

\begin{construction} \label{turnacompactumintoatopspace}
	If $K$ is a compactum, then we use the limit map $ \lambda_K \colon \beta(K) \to K $ to topologise $ K $ as follows.
	For any subset $ T \subseteq K $, we define the closure of $ T $ as the image $ \lambda_K(T^{\dag}) $.

	A subset $ Z \subseteq K $ is thus closed if and only if the limit of any ultrafilter relative to which $ Z $ is thick lies in $ Z $.
	Dually, a subset $ U \subseteq K $ is open if and only if it is thick with respect to any ultrafilter whose limit lies in $ U $.

	We denote the resulting topological space $ K^{\textit{top}} $.
	The assignment $ K \mapsto K^{\textit{top}} $ defines a lift $ \Alg(\beta) \to \Top $ of the forgetful functor $ \Alg(\beta) \to \Set $.
\end{construction}

\begin{proposition} \label{compactaarecompacta}
	The functor $ K \mapsto K^{\textit{top}} $ identifies the category of compacta with the category of compact Hausdorff topological spaces. 
\end{proposition}

We will spend the remainder of this section proving this claim.
Please observe first that $ K \mapsto K^{\textit{top}} $ is faithful.
What we will do now is prove:
\begin{enumerate}
	\item that for any compactum $ K $, the topological space $ K^{\textit{top}} $ is compact Hausdorff;
	\item that for any compact Hausdorff topological space $ X $, there is a $ \beta $-algebra structure $ K $ on the underlying set of $ X $ such that $ X \cong K^{\textit{top}} $; and
	\item that for any compacta $ K $ and $ L $, any continuous map $ K^{\textit{top}} \to L^{\textit{top}} $ lifts to a $ \beta $-algebra homomorphism $ K \to L$.
\end{enumerate}
To do this, it is convenient to describe a related idea: that of \emph{convergence} of ultrafilters on topological spaces.

\begin{definition} \label{limitpointofultrafilter}
	Let $ X $ be a topological space, and let $ x \in X $.
	We say that $ x $ is a \defn{limit point} of an ultrafilter $ \mu $ on (the underlying set of) $ X $ if and only if every open neighbourhood of $ x $ is $ \mu $-thick.
	In other words, $ x $ is a limit point of $ \mu $ if and only if, for every open neighbourhood $ U $ of $ x $, one has $ \mu \in U^{\dag} $.
\end{definition}

\begin{lemma} \label{opensetsarethickwrtultrafilters}
	Let $ X $ be a topological space, and let $ U \subseteq X$ be a subset.
	Then $ U $ is open if and only if it is thick with respect to any ultrafilter with limit point in $ U $.
\end{lemma}

\begin{proof}
	If $ U $ is open, then $ U $ is by definition thick with respect to any ultrafilter with limit point in $ U $.

	Conversely, assume that $ U $ is thick with respect to any ultrafilter with limit point in $ U $.
	Let $ u \in U $.
	Consider the set $ G \coloneq N(u) \cup \{ X \smallsetminus U \} $, where $N(u)$ is the collection of open neighbourhoods of $u$.
	If $ U $ does not contain any open neighbourhood of $u$, then no finite intersection of elements of $ G $ is empty.
	By \ref{generateultrafilters} there is an ultrafilter $ \mu $ supported on the $ N(u) \cup \{ X \smallsetminus U \} $, whence $ u $ is a limit point of $ \mu $, but $ U $ is not $ \mu $-thick.
	This contradicts our assumption, and so we deduce that $ U $ contains an open neighbourhood of $ u $.
\end{proof}

\begin{lemma} \label{continuityviaultrafilters}
	Let $ X $ and $ Y $ be topological spaces, and let $ \phi \colon X \to Y $ be a map.
	Then $ \phi $ is continuous if and only if, for any ultrafilter $ \mu $ on $ X $ with limit point $ x \in X $, the point $ \phi(x) $ is a limit point of $ \phi_{\ast}\mu $.
\end{lemma}

\begin{proof}
	Assume that $ \phi $ is continuous, and let $ \mu $ be an ultrafilter on $ X $, and assume that $ x \in X $ is a limit point of  $ \mu $.
	Now assume that $ V $ is an open neighbourhood of $ \phi(x) $.
	Since $ \phi^{-1}V $ is an open neighbourhood of $ x $, so it is $ \mu $-thick, whence $ V $ is $\phi_{\ast}\mu$-thick.
	Thus $ \phi(x) $ is a limit point of $ \phi_{\ast}\mu $.

	Assume now that if $ x \in X $ is a limit point of an ultrafilter $ \mu $, then $ \phi(x) $ is a limit point of $ \phi_{\ast}\mu $.
	Let $ V \subseteq Y $ be an open set.
	Let $ x \in \phi^{-1}(V) $, and let $ \mu $ be an ultrafilter on $ X $ with limit point $ x $.
	Then $ \phi(x) $ is a limit point of $ \phi_{\ast}\mu $, so $V$ is $ \phi_{\ast}\mu $-thick, whence $ \phi^{-1}(V) $ is $ \mu $-thick.
	It follows from \ref{opensetsarethickwrtultrafilters} that $\phi^{-1}(V)$ is open.
\end{proof}

\begin{lemma} \label{quasicompactiffeveryultrafilterhasalimitpoint}
	Let $ X $ be a topological space.
	Then $ X $ is quasicompact if and only if every ultrafilter on $ X $ has at least one limit point.
\end{lemma}

\begin{proof}
	Assume first that $ X $ is quasicompact.
	Let $ \mu $ be an ultrafilter on $ X $, and assume that $ \mu $ has no limit point.
	Select, for every point $ x \in X $, an open neighbourhood $ U_x $ thereof that is not $ \mu $-thick.
	Quasicompactness implies that there is a finite collection $ x_1, \dots, x_n \in X $ such that $ \left\{ U_{x_1}, \dots, U_{x_n} \right\} $ covers $ X $.
	But at least one of $ U_{x_1}, \dots, U_{x_n} $ must be $ \mu $-thick.
	This is a contradiction.

	Now assume that $ X $ is not quasicompact.
	Then there exists a collection $ G \subseteq \PP(X) $ of closed subsets of $ X $ such that the intersection all the elements of $ G $ is empty, but no finite intersection of elements of $ G $ is empty.
	In light of \ref{generateultrafilters}, there is an ultrafilter $ \mu $ with the property that every element of $ G $ is thick.
	For any $ x \in X $, there is an element $ Z \in G $ such that $ x \in X \smallsetminus Z $.
	Since $ Z $ is $ \mu $-thick, $ X \smallsetminus Z $ is not.
	Thus $ \mu $ has no limit points.
\end{proof}

\begin{lemma} \label{hausdorffiffeveryultrafilterhasatmostonelimitpoint}
	Let $ X $ be a topological space.
	Then $ X $ is Hausdorff if and only if every ultrafilter on $ X $ has at most one limit point.
\end{lemma}

\begin{proof}
	Assume that $ \mu $ is an ultrafilter with two distinct limit points $ x_1 $ and $ x_2 $.
	Choose open neighbourhoods $ U_1 $ of $ x_1 $ and $ U_2 $ of $ x_2 $.
	Since they are both $ \mu $-thick, they cannot be disjoint;
	hence $ X $ is not Hausdorff.

	Conversely, assume that $ X $ is not Hausdorff.
	Select two points $ x_1 $ and $ x_2 $ such that every open neighbourhoods $ U_1 $ of $ x_1 $ and $ U_2 $ of $ x_2 $ intersect.
	Now the set $ G $ consisting of open neighbourhoods of either $ x_1 $ \emph{or} $ x_2 $ has the property that no finite intersection of elements of $ G $ is empty.
	In light of \ref{generateultrafilters}, there is an ultrafilter $ \mu $ with the property that every element of $ G $ is thick.
	Thus $ x_1 $ and $ x_2 $ are limit points of $ \mu $.
\end{proof}

Let us now return to our functor $ K \mapsto K^{\textit{top}} $.

\begin{lemma} \label{limitsarelimits}
	Let $ K $ be a compactum, and let $ \mu $ be an ultrafilter on $ K $.
	Then a point of $ K^{\textit{top}} $ is a limit point of $ \mu $ in the sense of \ref{limitpointofultrafilter} if and only if it is the limit of $ \mu $ in the sense of \ref{compactaasbetaalgebras}.
\end{lemma}

\begin{proof}
	Let $ x \coloneq \lambda_K(\mu) $.
	The open neighbourhoods $ U $ of $ x $ are by definition thick (relative to $ \mu $), so certainly $ x $ is a limit point of $ \mu $.

	Now assume that $ y \in K^{\textit{top}} $ is a limit point of $ \mu $.
	To prove that the limit of $ \mu $ is $ y $, we shall build an ultrafilter $ \tau $ on $ \beta(K) $ with the following properties:
	\begin{enumerate}
		\item under the multiplication $ \beta^2 \to \beta $, the ultrafilter $ \tau $ is sent to $ \mu $; and
		\item under the map $ \lambda_{\ast} \colon \beta^2 \to \beta  $, the ultrafilter $ \tau $ is sent to $\delta_y$.
	\end{enumerate}
	Once we have succeeded, it will follow that
	\[
		\lambda_K( \mu ) = \lambda_K( \mu_{\tau} ) = \lambda_K(\lambda_{K,\ast}\tau) = \lambda_K(\delta_y) = y \comma
	\]
	and the proof will be complete.

	Consider the family $ G' $ of subsets of $ \beta(K) $ of the form $ T^{\dag} $ for a $ \mu $-thick subset $ T \subseteq S $;
	since these are all nonempty and they are stable under finite intersections, it follows that no finite intersection of elements of $ G' $ is empty.

	Now consider the set $ G \coloneq G' \cup \{ \lambda_K^{-1}\{y\} \}$.
	If $ T $ is $ \mu $-thick, then we claim that there is an ultrafilter $ \nu \in \lambda_K^{-1}\{y\} \cap T^{\dag} $.
	Indeed, consider the set $ N(y) \cup \{T\} $, where $ N(y) $ is the collection of open neighbourhoods of $ y $.
	Since every open neighbourhood of $ y $ is $ \mu $-thick, no intersection of an open neighbourhood of $ y $ with $ T $ is empty.
	By \ref{generateultrafilters} there is an ultrafilter supported on $ N(y) \cup \{T\} $, which implies that no finite intersection of elements of $ G $ is empty.

	Applying \ref{generateultrafilters} again, we see that $ G $ supports an ultrafilter $ \tau $ on $ \beta(K) $.
	For any $ T \subseteq K $,
	\[
		\mu_{\tau}(T) = \tau(T^{\dag}) \comma
	\]
	so since $ \tau $ is supported on $ G' $, it follows that $ \mu_{\tau} = \mu $.
	At the same time, since $ \tau $ is supported on $ \{\lambda_K^{-1}\{y\}\} $, it follows that $ \{y\} $ is thick relative to $ \lambda_{K,\ast}\tau $, whence $ \lambda_{K,\ast}\tau = \delta_y $.
\end{proof}

\begin{proof}[Proof of \ref{compactaarecompacta}]
	Let $ K $ be a compactum.
	Combine \ref{hausdorffiffeveryultrafilterhasatmostonelimitpoint,quasicompactiffeveryultrafilterhasalimitpoint,limitsarelimits} to conclude that $ K^{\textit{top}} $ is a compact Hausdorff topological space.

	Let $ X $ be a compact Hausdorff topological space with underlying set $ K $.
	Define a map $ \lambda_K \colon \beta(K) \to K $ by carrying an ultrafilter $ \mu $ to its unique limit point in $ X $.
	This is a $ \beta $-algebra structure on $ X $, and it follows from \ref{limitsarelimits} and the definition of the topology together imply that $ X \cong K^{\textit{top}}$.

	Finally, let $ K $ and $ L $ be compacta, and let $ \phi \colon K^{\textit{top}} \to L^{\textit{top}} $ be a continuous map.
	To prove that $ \phi $ is a $ \beta $-algebra homomorphism, it suffices to confirm that if $ \mu $ is an ultrafilter on $ K $, then
	\[
		\lambda_L (\phi_{\ast} \mu) = \phi (\lambda_K(\mu)) \comma
	\]
	but this follows exactly from \ref{continuityviaultrafilters}.
\end{proof}

\begin{nul}
	We opted in \ref{turnacompactumintoatopspace} to define the topology on a compactum $ K $ in very explicit terms, but note that the map $ \lambda_K \colon \beta(K) \to K^{\textit{top}} $ is a continuous surjection between compact Hausdorff topological spaces.
	Thus $ K^{\textit{top}} $ is endowed with the quotient topology relative to $ \lambda_K $.
\end{nul}


