%!TEX root = book.tex 
% chktex-file 1
% chktex-file 3
% chktex-file 8
% chktex-file 12
% chktex-file 18
% chktex-file 24
% chktex-file 35 
% chktex-file 42

\chapter{Set theory \& cardinals}%
\label{cha:cardinals}

Mathematicians' \enquote{stock} set theory, $\zfc$
(Zermelo--Fraenkel set theory $\zf$ plus the Axiom of Choice $\ac$)
doesn't quite have the expressive power one needs for work with categories and higher categories.
The issue ultimately comes down to Cantor's diagonal argument:
there is no surjection of a set onto its powerset.
This is ultimately why no one can contemplate a set of all sets,
and it's also the key to Freyd's observation that
if $C$ is a category and $\kappa$ is the cardinality of its set of arrows,
then $C$ has all $\kappa$-indexed products only if $C$ is a poset.
This, in turn, is what's behind the \enquote{solution set condition}
in representability theorems or the Adjoint Functor Theorem.
Hence one really must distinguish between \enquote{large} and \enquote{small} objects.

One improves matters by passing to von Neumann--Bernays--Gödel set theory ($\nbg$),
which is a conservative extension of $\zfc$.
In $ \nbg $, the formal language consists of the symbols $\in$ and $=$;
a constant $V$; suitable variables;
the usual connectives of first-order logic ($\neg$, $\wedge$, $\vee$, $\implies$, and $\iff$);
and the quantifiers $\forall$ and $\exists$.
The objects of the theory are called \defn{classes}.
A class $ x $ is called a \defn{set} if and only if $x \in V$;
a \defn{proper class} is a class $ X $ such that $ X \notin V $.
We summarize the axioms of $ \nbg $ in informal language:
\begin{description}
	\item[\textbf{Extensionality}] Classes $ X $ and $ Y $ are equal if and only if,
		for any $ z $, one has $ z \in X $ if and only if $ z \in Y $.
	\item[\textbf{Regularity}] For every class $ X $,
		there exists an element $ z \in X $ such that $ z \cap X = \varnothing $.
	\item[\textbf{Infinity}] There is an infinite set.
	\item[\textbf{Union}] If $ x $ is a set, then $ \bigcup x = \bigcup_{z \in x} z $ is a set as well.
	\item[\textbf{Pairing}] If $ x $ and $ y $ are sets, then $ \{x,y\} $ is a set as well.
	\item[\textbf{Powerset}] If $ x $ is a set, then the powerset $ P(x) $ is a set as well.
	\item[\textbf{Limitation of size}] A class $X$ is a proper class if and only if
		there is a bijection between $X$ and $V$.
	\item[\textbf{Class comprehension}] For every first-order formula $ \phi(x) $ with a free variable $ x $ in which the quantifiers are over sets,
		there exists a class $ \{ x \in V : \phi(x) \} $ whose elements are exactly those sets $ x $ such that $ \phi(x) $.
\end{description}

In matters of set theory,
we will generally follow the notations and terminological conventions
of the comprehensive monograph of \cite{Jech2003}.
We will also refer to the texts of \cite{Drake1974} and \cite{Kanamori2009}.
In particular, $ \Ord $ denotes the proper class of ordinal numbers.
For any ordinal $ \alpha $, the set $ V_{\alpha} $ is defined recursively as follows:
\begin{enumerate}
	\item If $ \alpha = 0 $, then $ V_{\alpha} \coloneq \emptyset $;
	\item if $ \alpha = \beta + 1 $ for an ordinal number $ \beta $, then $ V_{\alpha} \coloneq P(V_{\beta}) $;
	\item if $ \alpha $ is a limit ordinal, then $ V_{\alpha} \coloneq \bigcup_{\beta < \alpha} V_{\beta} $.
\end{enumerate}
If $ x $ is a set, then the \defn{rank} of $ x $ is the smallest ordinal number $ \alpha $ such that $ x \in V_{\alpha} $.
The proper class $ V $ is then the union $ \bigcup_{\alpha \in \Ord} V_{\alpha} $.

In matters of (higher) category theory,
we will generally follow the notations and terminological conventions
of \cite{Lurie2009}.
However, our set-theoretic conventions are slightly different:
\begin{definition}
	A \defn{large-category}%
	\footnote{We use the term \enquote{category}
		for what other authors might call
		\enquote{$ \infty $-category},
		\enquote{$(\infty,1)$-category}, or
		\enquote{quasicategory}.
		We will use the term \enquote{1-category}
	when the specification is needed.}
	$C$ consists of a sequence $(C_n)_{n\in\NN_0}$ of classes,
	along with a family of class maps $ \phi^{\ast} \colon C_m \to C_n $
	for each map $ \phi \colon n \to m $,
	subject to all the formulas that express the statement that $C_n$ is a simplicial class
	that satisfies the inner Kan condition.

	If the large-category $C$ contains a full subcategory $ C' \subseteq C $
	such that each $ C'_n $ is a set and
	such that every object of $ C $ is equivalent to an object of $ C' $,
	then we will call $ C $ a \defn{category}
	or, for emphasis, a \defn{small category}.%
	\footnote{These are sometimes called \defn{essentially small}.}
	
	A large-category $ C $ is said to be \defn{locally small} if and only if,
	for every subset $ C'_0 \subseteq C_0$,
	the full subcategory $ C' \subseteq C $ spanned by the elements of $ C'_0 $ is small.
	
	Limits and colimits are only considered for functors $ J \to C $ in which
	the $ J $ is a small category.
	Hence when we refer to \defn{all limits} or \defn{all colimits},
	we mean all limits or colimits of diagrams indexed on small categories.
	
	If $ C $ is a category and $ D $ is a large-category, 
	then the large-category $ \Fun(C, D) $ is defined in the usual way,
	so that $ \Fun(C, D)_n $ is the class of simplicial maps
	$ C \times \Delta^n \to D $.
\end{definition}

\begin{notation}%
	\label{not:Vsetsanimaepresheavescategories}
	We shall write $ \Set^V $ for the large-category of all sets.
	The objects of $ \Set^V$ are thus precisely the elements of $V$.

	We shall write $ \An^V $ for the large-category of all animae.%
	\footnote{We follow Clausen and Scholze,
		and we use the term \enquote{anima} for
		what other authors might call
		\enquote{space},
		\enquote{$ \infty $-groupoid}, or
		\enquote{$ (\infty,0) $-category}.}	
	The objects of $ \An^V $ are thus precisely
	the Kan complexes $ \Delta^{\op} \to \Set^V $.

	If $ C $ is a category, then
	we shall write $ \PP^V(C) \coloneq \Fun(C^{\op}, \An^V) $
	and $ \tau_0\PP^V(C) \coloneq \Fun(C^{\op}, \Set^V) $.
	We will write
	\[ \yo \colon C \inclusion \PP^V(C) \]
	for the Yoneda embedding $ X \mapsto \yo_X $.
	Thus if $ X $ is an object of $ C $, then
	$ \yo_X \colon C^{\op} \to \An^V $ is
	the functor represented by $ X $, so that
	$ \yo_X(U) = \Map(U, X) $.

	We shall write $ \Cat^V $ for the large-category of all categories.
	The objects of $ \Cat^V $ are thus precisely
	the weak Kan complexes $ \Delta^{\op} \to \Set^V $.
\end{notation}

The Class Comprehension Axiom Schema implies the \defn{Axiom of Global Choice},
which ensures the existence of a choice function $ \tau \colon V \to V $ such that $ \tau(x) \in x $.
One needs this to make sense of a construction
like \enquote{the} functor $ - \times u \colon C \to C $ for a large-category $ C $
with all finite products and a fixed object $ u \in C $.

Here, we will work with $\nbg$ as our base theory,
so that we may speak of proper classes and large-categories
whenever the occasion arises.

However, the whole project of higher category theory turns on the principle that
we want to be able to deal with the collections of all objects of a given kind
as a mathematical object in its own right,
and that the passage up and down these category levels
is a fruitful way to understand even completely \enquote{decategorified} objects.%
\footnote{The \emph{microcosm principle} of Baez--Dolan is a
precise illustration of this principle.} 
If we have a large-category $C$,
$ \nbg $ provides us with no mechanism
to view $C$ itself as an object
of a still larger category of all categories.
This limits the kinds of operations we are permitted to do to $ C $.

To give ourselves the room to pass up and down category levels,
we need to have a hierarchy of \enquote{scales} at which we can work.
These scales will be identified by inaccessible cardinals
or, equivalently, Grothendieck universes.
The existence of these cardinals is independent of $ \nbg $.

But now a different sort of concern arises.
We will also want to have assurance
that the results we obtain at one scale remain valid at other scales.
We might prefer to prove sentences about
\emph{all} sets, animae, groups, etc. --
not just those within a universe.
This sort of \enquote{scale-invariance of truth}
is expressed by a \defn{reflection principle} (\ref{sec:reflection_principles}).
The reflection principle we will use here states roughly that
there is an inaccessible cardinal $ \kappa $ such that
statements of set theory hold in the universe $ V_{\kappa} $
just in case they hold in $V$ itself.
This is the \defn{Lévy scheme} $ \levy $,
which we will first formulate as a large cardinal axiom.
In effect, this permits us to focus our attention on \emph{categories}
(as opposed to large-categories).
This scheme has a strictly higher conistency strength
than the existence of a proper class of inaccessible cardinals;
however, its consistency strength is strictly lower
than that of the existence of a single Mahlo cardinal.

\input{regularityandsmallness.tex}

\input{accessibilityandpresentability.tex}

\input{stronglimitandinaccessiblecardinals.tex}

\input{echelonsofaccessibility.tex}

\input{indization.tex}

\input{higherinaccessibility.tex}

