%!TEX root = book.tex 
% chktex-file 1
% chktex-file 3
% chktex-file 8
% chktex-file 12
% chktex-file 18
% chktex-file 24
% chktex-file 35 
% chktex-file 42

%-------------------------------------------------------------------%
%-------------------------------------------------------------------%
%-------------------------------------------------------------------%
\chapter{Grothendieck's homotopy hypothesis}%
\label{cha:Grothendieckshomotopyhypothesis}
%-------------------------------------------------------------------%
%-------------------------------------------------------------------%
%-------------------------------------------------------------------%

The mission of homotopy theory is to iteratively enhance every \emph{property} of a mathematical object to \emph{structure} on it.
The homotopy theorist deconstructs the equals sign by this process:
they no longer regard \enquote{$x = y$} as a property that $x$ and $y$ together possess,
but rather as piece of structure that connects $x$ and $y$.
That structure is then a \emph{path} between $x$ and $y$.
Semantically, we consider this path as a \emph{reason} for -- or as a \emph{witness} to -- the equality \enquote{$x = y$}.

If $\alpha$ and $\beta$ are paths connecting $x$ and $y$,
then again we do not wish to speak of \enquote{$\alpha = \beta$} as a property,
but as a further piece of structure -- a \emph{homotopy} between $\alpha$ and $\beta$.
We iterate: two homotopies are no longer merely \enquote{equal}, but they may be connected by \emph{higher homotopies};
two higher homotopies may be connected by further higher homotopies, \emph{etc}., \emph{etc}., \emph{ad infinitum}.

The data of all these points and paths and homotopies and higher homotopies, taken together, constitute an \emph{anima} (plural: \emph{animae}).
Animae are also called \emph{spaces}, \emph{homotopy types}, \emph{Kan complexes}, or \emph{$\infty$-groupoids}.
These terms each reflect a certain attitude toward these objects.
The terms \enquote{space} and \enquote{homotopy type} acknowledge that these objects were first modelled and understood using topological spaces and topological notions of homotopy.
A \enquote{Kan complex} is then a combinatorial blueprint for these homotopies and their relations.
The phrase \enquote{$\infty$-groupoid} then reinterprets the (higher) homotopies as (higher) \emph{symmetries}.
The fact that these terms can all be used interchangeably is a nontrivial insight -- Grothendieck's \emph{homotopy hypothesis}.
We will formulate and prove a version of this sentence in this chapter -- surely not the version Grothendieck had in mind,
but one that is better-adapted to the needs of contemporary mathematicians.
In our formulation, it becomes a theorem of Kan.

Our adoption of \enquote{anima} reflects our desire not to favor any one of these attitudes.
Animae are for us fundamental objects:
they play the same role in \emph{homotopical mathematics} that sets play in `ordinary' mathematics.
In ordinary set-theoretic mathematics, every object is ultimately defined in terms of sets;
similarly, every object in homotopical mathematics is defined in terms of animae.

Symmetries of objects were certainly central to the mathematics of the 19th century, but
it's a distinctly 20th century concept that symmetries might meaningfully have their own symmetries.
(It is interesting to consider the origins of this idea, but
it would be difficult to pinpoint the first person who seriously considered it.)
In any case, the 20th century provided three realizations about homotopy theory's iterative enhancement process.

\begin{enumerate}
  \item%
    Foremost was the promise of interesting new phenomena to study.
    Homological algebra appears at first to be a relatively featureless outgrowth of linear algebra.
    The Bockstein homomorphism is an early illustration that ordinary modules interact in new ways in derived settings.
    But it's the nontriviality of the Hopf element $\eta$ in the stable homotopy group $\pi^s_1$ that decisively separates \emph{homological algebra} -- ordinary algebra that is then derived -- from \emph{homotopical algebra} -- algebra done in a natively homotopical setting.
    The first signal from the mysterious world of homotopical algebra was a short message: \enquote{$\eta \neq 0$}.
  \item%
    In spite of our informal description of homotopy theory as an inductive enhancement of properties into structure,
    by the middle of the 20th century, the idea had been made precise, and
    it had become part of the standard toolkit of algebraic topology.

    In fact, it can now be made precise in a number of different ways.
    On one hand, we can model homotopical structures entirely via ordinary mathematical objects.
    We could, for example, model them using topological structures.
    For reasons we discuss below, we will adopt the Kanian approach and encode homotopical structures using \emph{simplicial diagrams}.

    Alternatively -- and in a spirit closer to that of this introduction -- one might instead attempt to rewrite the logical foundations of mathematics in a way that bakes in our preference for structure over properties.
    This is the approach of \emph{homotopy type theory}, a stirring vision of new foundations in mathematics.
    As of this writing, homotopy type theory is still in its infancy.
    In later editions of this book, perhaps the combinatorics of simplices will be replaced by fundamental facts about type theory.
  \item%
    Once it was understood how to model homotopical structures accurately, new questions arose:
    \emph{how do we construct models that are maximally useful?}
    \emph{what does it mean to say that two models represent the same homotopy theory?}
    \emph{shouldn't this notion of sameness, whatever it is, be subject to the same inductive refinement process that got us here?}
    These questions lay at the heart of the many foundational developments in homotopy theory starting in the 1970s.

    By the end of the millennium it was clear that one would need to take a further step, and contemplate a \emph{homotopy theory of homotopy theories}.
    Just as Grothendieck had seen that ordinary homotopy theory should be equivalent to the theory of $\infty$-groupoids,
    Joyal, Kan, Rezk, Simpson, and Toen all recognized that the homotopy theory of homotopy theories should be equivalent to the theory of \emph{$\infty$-categories}.
\end{enumerate}

Our approach to constructing the homotopy theory of animae follows a general recipe, which will inform our work throughout this book.
The recipe provides a strategy for designing a homotopy theory $\EE$, using only partial or imperfect information about it:
\begin{enumerate}
  \item%
    Select a piece $\EE_0$ of $\EE$ that is simple enough that you can understand it completely,
    but complex enough so that any object $X \in \EE$ is completely determined by the sets/groups/whatevers of maps $T \to X$ with $T \in \EE_0$.
    In many cases, you'll want $\EE_0$ to generate $\EE$ under suitable colimits.
  \item%
    Now select a small category $J$, usually combinatorial in nature,
    along with an essentially surjective functor $R \colon J \to \EE_0$ (which need not be fully faithful).
    In many cases, it will be helpful if the objects of $J$ come equipped with some notion of \emph{degree}.
    The category $J$ and functor $R$ should be chosen so that some key salient features of general objects $X \in \EE$ can be read off from mapping objects $\Map(R(j),X)$.
  \item%
    Encode these salient features as a set of properties $P$ of the corresponding functors $\Map(R(-),X)$.
    For example, perhaps you'll want to require that for some particular $j \in J$, the object $\Map(R(j),X)$ is trivial.
    Or perhaps such a property expresses $\Map(R(k),X)$ as a limit or colimit of various other mapping objects $\Map(R(j),X)$.
    The objects of your homotopy theory will be exactly the functors $J^{\op} \to \Set$ (or other enriching category) that enjoy these properties of $P$.
\end{enumerate}

In this chapter, we will construct the homotopy theory of animae in this way:
$\EE_0$ will be the homotopy theory of contractible animae (which is trivial),
$J$ is the category of \emph{simplices} $\DDelta$ (defined below),
and $P$ is Kan's \emph{horn-filling condition}.

Other options for $J$ (and therefore $P$) are possible:
there is an interesting class of categories -- the \emph{test categories} -- that can stand in for $\DDelta$. 
These include the category of nonempty finite sets, Joyal's categories $\Theta_n$, as well as various categories of cubes and trees.

One special feature of $\DDelta$ is that it can also be used to define the larger homotopy theory of $\infty$-categories itself.
For this homotopy theory, $\EE_0$ is the homotopy theory of finite ordinals (which is not trivial, but is nevertheless very simple),
$J$ is again the category $\DDelta$,
and $P$ is the \emph{inner horn-filling condition} first identified explicitly by Boardman--Vogt.



\input{simplicial}

\input{constructions}
